---
title: "Bachelor's Thesis Presentation"
subtitle: "The Influence of the Investment Horizon on the Asset Allocation"
author: "Joël Meili & Fabio Bührer"
institute: Zurich University of Applied Sciences Winterthur
date: "July 1st 2019"
output:
  beamer_presentation:
    slide_level: 2
    theme: "AnnArbor"
    colortheme: "dolphin"
    fonttheme: "structurebold"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE, results = FALSE, fig.height = 4)
```

```{r load_libraries}
library(car)
library(ghyp)
library(dplyr)
library(tidyr)
library(lubridate)
library(ggplot2)
library(ggthemes)
library(kableExtra)
```

```{r load_data}
path <- "~/Dropbox/BA18/data/"
load(paste0(path, "log.return.assets.Rdata"))
load(paste0(path, "params.symm.Rdata"))
load(paste0(path, "fitted.parameters.Rdata"))
load(paste0(path, "allocation.Rdata"))
load(paste0(path, "opt.weights.Rdata"))
assets.yearly <- assets %>% gather(Asset, Value, 2:ncol(assets)) %>% group_by(Year = year(Date), Asset) %>% summarise(Value = sum(Value)) %>% spread(2, 3)
```

## Contents
- Goals of research
- Aspects of portfolio optimization
- Problems with the normality assumption
- Parameter fitting of financial log-returns
- Results
- Conclusion
- Discussion

## Goals of the Research
- Understand the role of the investment horizon in portfolio allocation
- Establishing a risk measure
- Building a model for the evolution of assets' value
- Modeling fat tails of financial assets

# Aspects of Portfolio Optimization
## Risk Measures
### Standard deviation
- Risk quantified by movements from the mean (volatility), no level of confidence applicable
- Does not capture skewness or kurtosis (fat tails), but is coherent

### Value-at-risk
- Intuitive indication of potential losses, level of confidence applicable
- Does capture skewness and kurtosis (fat tails), but is not coherent

### Expected shortfall
- Intuitive indication of potential losses, level of confidence applicable
- Does capture skewness and kurtosis (fat tails) and is coherent

### Our solution in this thesis
- Use value-at-risk or expected shortfall as risk measures

## Mean-Variance Analysis

### What is mean-variance analysis
- Optimization of weights to find efficient frontier (lowest portfolio standard deviation for given portfolio return)

### Advantages
- Easy computation
- Explicit results (weights)

### Disadvantages
- Drawbacks of standard deviation as a risk measure
- No consideration of desired investment horizon

## Fat Tails in Financial Returns: Basics
- In fat-tailed data, extreme movements are relatively frequent (compared to thin-tailed distribution)
- Thin-tailed distributions decay like $O(e^{-\lambda|x|}), \lambda \in \mathbb{R}_{>0}$
- Fat-tailed distributions decay like $O(|x|^{-\alpha}), \alpha \in \mathbb{R}_{>0}$
- Thin-tailed or fat-tailed model: choice can make huge difference in portfolio optimization

### Heavy-tailed
- Distributions are called "heavy-tailed" or "fat-tailed" when the tails decay like a power law $O(|x|^{-\alpha}), \alpha \in \mathbb{R}_{>0}$

### Our solution in this thesis

- Use of the Student's t-distribution and generalized hyperbolic distributions

# Problems with the Normality Assumption
## Kurtosis and Skewness of Log-Returns
- Log-returns are often heavy tailed (kurtosis) especially for short-term horizons
- Stocks are usually negatively skewed and safe haven instruments e.g. JPY/USD are usually positively skewed

```{r, echo = FALSE}
par(mfrow = c(1, 2))
qqPlot(assets$SP500 %>% scale(), ylab = "sample quantile", main = "Daily S&P500 log-returns")
qqPlot(assets$JPY_USD %>% scale(), ylab = "sample quantile", main = "Daily JPY/USD log-returns")
```

## Kurtosis and Skewness of Log-Returns
- Effect of kurtosis is reduced significantly when the horizon is increased (aggregated log-returns)
- Assumption of normally distributed log-returns seems appropriate

```{r, echo = FALSE}
par(mfrow = c(1, 2))
qqPlot(assets.yearly$SP500%>% scale(), ylab = "sample quantile", main = "Yearly S&P500 log-returns")
qqPlot(assets.yearly$JPY_USD %>% scale(), ylab = "sample quantile", main = "Yearly JPY/USD log-returns")
```

## Tail Correlation (Gaussian vs. Student's t Copula)
- Multivariate log-return modelling implies tail correlation
- Tail correlation incorporates nonlinear dependencies that cannot be modeled solely with the covariance matrix

### Bivariate Gaussian Probability Density
$$f(\vec{x})=\frac{1}{2\pi}\det{\Sigma}^{-\frac{1}{2}}e^{-\frac{1}{2}(\vec{x}-\vec{\mu})'\Sigma^{-1}(\vec{x}-\vec{\mu})}$$
Where $\mu$ is the location vector and $\Sigma$ is the covariance matrix.

### Bivariate Student's t Probability Density
$$f(\vec{x})=\frac{\Gamma{\frac{\nu+2}{2}}}{\Gamma{\frac{\nu}{2}}\nu\pi|\Sigma|^{\frac{1}{2}}}[1+\frac{1}{\nu}(\vec{x}-\vec{\mu})^T\Sigma^{-1}(\vec{x}-\vec{\mu)}]^{-\frac{(\nu+2)}{2}}$$
Where $\Gamma$ is the gamma function and $\nu$ is the degrees of freedom parameter.

## Tail Correlation (Gaussian vs. Student's t Copula)
- The probability density function of a copula is defined by the Sklar's theorem
- The Gaussian copula diverges only in two of the corners whereas the Student's t copula diverges in all four corners

#### Sklar's Theorem
$$c(\vec{x})=\frac{f(\vec{x})}{\overline{f}(x_1)\overline{f}(x_2)}$$
Where $\overline{f}(x)$ is the univariate probability density function.

## Tail Correlation (Gaussian vs. Student's t Copula)
```{r, echo = FALSE}
x <- seq(-10, 10, by = 0.1)
y <- x
n <- gauss(mu = rep(0, 2), sigma = matrix(c(1, 0.5, 0.5, 1), ncol = 2, byrow = TRUE))
t <- student.t(nu = 2.5, mu = rep(0, 2), sigma = matrix(c(1, 0.5, 0.5, 1), ncol = 2, byrow = TRUE), gamma = rep(0, 2))  
norm <- function(x, y){dghyp(cbind(x, y), object = n, logvalue = TRUE) - dghyp(x, object = n[1], logvalue = TRUE) - dghyp(y, object = n[2], logvalue = TRUE)}
tn <- function(x, y){dghyp(cbind(x, y), object = t, logvalue = TRUE) - dghyp(x, object = t[1], logvalue = TRUE) - dghyp(y, object = t[2], logvalue = TRUE)}
z.norm <- outer(x, y, norm)
z.t <- outer(x, y, tn)
par(mfrow = c(1, 2))
contour(x, y, z.norm, main = "Gaussian log-copula")
contour(x, y, z.t, main = "Student's t log-copula")
```

# Parameter Fitting of Financial Log-Returns
## Univariate Symmetric Student's t-Distribution
- Fitted univariate symmetric Student's t-distributions to financial assets using a likelihood maximization algorithm described in the GHYP-package (\url{https://CRAN.R-project.org/package=ghyp})
- Bootstrapped N = 100 samples to evaluate confidence interval for estimates of $\nu$

```{r, results = "asis"}
mu <- apply(params.symm, 2, mean)
sig <- apply(params.symm, 2, sd)
mat <- sapply(1:ncol(params.symm), FUN = function(x){
  mu[x] + c(-1, 0, 1)*sig[x]
})
colnames(mat) <- c("$\\nu_{DIJA}$", "$\\nu_{S\\&P500}$", "$\\nu_{10Y US Bond Futures}$", "$\\nu_{JPY/USD}$", "$\\nu_{GOLD}$")
rownames(mat) <- c("$\\overline{\\mu}-\\overline{\\sigma}$", "$\\overline{\\mu}$", "$\\overline{\\mu}+\\overline{\\sigma}$")
mat <- round(mat, digits = 3)
kable(mat, escape = FALSE) %>% kable_styling()
```

## Symmetric vs. Skewed Student's t-Distribution
- Both variants have fat-tailed distributions
- Symmetric Student's t-distribution does not allow intrinsic skewness of some instruments
- Skewed Student's t-distribution is a generalized version of symmetric distribution
- Skewed Student's t-distribution's skewness parameter dictates degree of asymmetry
- Negative skewness: left tail is fatter (risky assets)
- Positive skewness: right tail is fatter (hedge assets)

## Graphical Assessment of Goodness of Fit for Univariate Skewed Student's t-Distribution
- Skewed Student's t-distribution captures extreme events in the tails better than symmetric Student's t-distribution
- Graphical assessment provides further motivation for the use of the skewed Student's t-distribution

```{r}
temp <- apply(assets[, 2:ncol(assets)], 2, scale)
temp <- apply(temp, 2, FUN = function(x) x[order(x)])
N <- nrow(temp)
fit.sp500 <- fit.tuv(temp[, 2], silent = TRUE)
fit.sp500.symm <- fit.tuv(temp[, 2], symmetric = TRUE, silent = TRUE)
fit.jpy <- fit.tuv(temp[, 4], silent = TRUE)
fit.jpy.symm <- fit.tuv(temp[, 4], symmetric = TRUE, silent = TRUE)
par(mfrow = c(1, 2))
plot(log(1:N/(N + 1))~temp[, 2], xlim = c(min(temp[, 2]), 0), xlab = "S&P500", ylab = "log(P(X<x)")
lines(log(pghyp(temp[, 2], object = fit.sp500))~temp[, 2], col = 2)
lines(log(pghyp(temp[, 2], object = fit.sp500.symm))~temp[, 2], col = 3)
lines(log(pnorm(temp[, 2], mean = mean(temp[, 2]), sd = sd(temp[, 2])))~temp[, 2], col = 4)
legend("topleft", legend = c("sample", "skewed t", "symmetric t", "normal"), col = 1:4, lty = 1, cex = 0.5)
plot(log((N + 1 - 1:N)/(N + 1))~temp[, 2], xlim = c(0, max(temp[, 2])), xlab = "S&P500", ylab = "log(1 - P(X<x))")
lines(log(1 - pghyp(temp[, 2], object = fit.sp500))~temp[, 2], col = 2)
lines(log(1 - pghyp(temp[, 2], object = fit.sp500.symm))~temp[, 2], col = 3)
lines(log(1 - pnorm(temp[, 2], mean = mean(temp[, 2]), sd = sd(temp[, 2])))~temp[, 2], col = 4)
legend("topright", legend = c("sample", "skewed t", "symmetric t", "normal"), col = 1:4, lty = 1, cex = 0.5)
```

## Multivariate Skewed Student's t-Distribution
- Fitted a multivariate skewed Student's t-distribution to financial assets using an expectation maximization algorithm described in the GHYP-package (\url{https://CRAN.R-project.org/package=ghyp})
- Again bootstrapped N = 100 samples to evaluate confidence interval for the parameter estimates

```{r, results = "asis"}
mu <- apply(params, 1, mean)
sig <- apply(params, 1, sd)
mat <- sapply(1:nrow(params), FUN = function(x){
  mu[x] + c(-1, 0, 1)*sig[x]
})
colnames(mat) <- c("$\\nu$", "$\\gamma_{DIJA}$", "$\\gamma_{S\\&P500}$", "$\\gamma_{10Y US Bond Futures}$", "$\\gamma_{JPY/USD}$", "$\\gamma_{GOLD}$")
rownames(mat) <- c("$\\overline{\\mu}-\\overline{\\sigma}$", "$\\overline{\\mu}$", "$\\overline{\\mu}+\\overline{\\sigma}$")
mat <- round(mat, digits = 3)
kable(mat, escape = FALSE) %>% kable_styling()
```

# Results
## Portfolio Optimiztion Using Normal and Non-Normal Distributions
- Optimal portfolio weights are the same for normal and non-normal distributions as long as standard deviation is used as risk measure (same variance for distributions), independent of horizon
- Optimal portfolio weights are the same for standard deviation, value-at-risk or expected shortfall optimized portfolio when normal distributions are used, independent of horizon
- Different portfolio weights when non-normal distributions and value-at-risk or expected shortfall are used as risk measure, dependent of horizon

## Monte Carlo Simulation of Univariate Symmetric Student's t-Distributed Log-Returns
- Value-at-risk optimization for simulated univariate symmetric Student's t-distributed log-returns
- Used aggregated log-returns and adjusted value-at-risk level ($\alpha=1-\frac{\tau}{26000}$)

### Relationship between $\tau$ and $\alpha$
- $\alpha$ is chosen to cover losses that occur once in a century for each $\tau$, such that results are comparable

## Monte Carlo Simulation of Univariate Symmetric Student's t-distributed Log-Returns
```{r, echo = FALSE}
horizons <- rownames(weights)
weights <- as.data.frame(weights)
weights$Horizon <- horizons
weights$Horizon <- factor(weights$Horizon, levels = c("daily", "weekly", "monthly", "yearly"))
weights <- weights %>% gather(DoF, Weight, 1:(ncol(weights) - 1))
weights$DoF <- sapply(weights$DoF, FUN = function(x) strsplit(x, "=")[[1]][2])
weights$DoF <- factor(weights$DoF, levels = c("2.5", "3", "4", "5", "7", "10", "20", "Inf"))
ggplot(weights, aes(x = Horizon, y = Weight, fill = DoF))+
  geom_bar(stat = "identity")+
  theme_classic()
```

## Portfolio Optimization Using the Multivariate Skewed Student's t-Distribution
- The assets are described by a multivariate skewed Student's t-distribution with 3.5 degrees of freedom
- Expected shortfall of the portfolio is optimized at various confidence levels using the concept of linearity of the marginal distributions, the same relationship between $\tau$ and $\alpha$ persists

### Conservative assumption
- Number of degrees of freedom does not increase as horizon is increased

## Portfolio Optimization Using the Multivariate Skewed Student's t-Distribution

```{r, echo = FALSE}
ggplot(opt.weights, aes(x = Days, y = Weight, fill = Asset))+
  geom_area()+
  scale_x_log10()+
  theme_classic()
```

## Conclusion
- Assumption of normally distributed log-returns is invalid, especially for short-term investments
- Kurtosis and skewness are relevant quantities in portfolio optimization
- Optimal portfolio weights are dependent of the horizon when non-normal distributions and value-at-risk or expected shortfall are used for optimization
- The skewed Student's t-distribution is a good proxy for modelling log-returns
- Long-term investors can and should take more tail risks than short-term investors

## Discussion
- Q&A
- Suggestions
- Feedback